\documentclass{article}
\usepackage{url}


\author{Kenneth Hansen}
\title{Latex assignment - Part One}

\begin{document}
\maketitle

\section{Requirements of Bachelor thesis}
The bachelor’s project must document the student’s understanding of and ability to reflect on the practices of the profession and the use of theory and methods in relation to a real-life problem.
\cite[pg.18]{studieordning} \\
To achieve this the strudment must investigate a software related problem, find a solution, and make small implementation of the solution to demenstrate it. The student should try to include elements from his/hers clases the student have had during the program. The Project can be done in groups of up to 4 peaople, the bigger the group the bigger the scope the project has to be. 
\cite[pg.1]{bachelorProject} \\
\subsection{Requirements of the report}
\begin{enumerate}
    \item The report has a maximun size. The max size of the report is calculated by this formula: \(maxPageCount = 40 + 20·numberOfStudents\) \cite[pg.1]{studieordning}
    \item The report must be written en either Danish or English \cite[pg.1]{bachelorProject}
    \item The content itself must include a thorough description of the work done druing the project and also an evaluation and reflection of the work done \cite[pg.2]{studieordning}
  \end{enumerate}

  \subsection{Report content}
  These are the required components of the report itself
  \begin{enumerate}
    \item The report first page(cover) has to have a title, with the students name, ID, school and supervisor
    \item The report must have an abstract that is sort of an advertisement of the project and answers these questions:
    \begin{itemize}
        \item What is the problem?
        \item Why is the problem interesting?
        \item What is the solution?
        \item What are the implications of the solution?
    \end{itemize}
    \item The report must have an Introduction that desribes why the topic is important today, what the objectives of the project is(The expected result), project taskes(How do you reach the expected result, what tasks must you acomplish to reach the expected result), Scope of the project(what is the objectives and what is not), and a brief description of:
    \begin{itemize}
        \item State of the art and trends - a description of current and similiar solutions in the area chosen.
        \item Requirements specification and solution design - a formulation of project foundation and detailed description of the solution.
        \item Solution development and implementation - A presentation of the implemented solution, how it was deployed and how it is mantained.
        \item Conclusions - What has been done and what you have found out.
        \item Appendices - A list of references of used information sources.
        \item Final work - A visual powerpoint must be done to demonstrate and presentate the work done, and a small demo of the application.
    \end{itemize}
  \end{enumerate}
  \cite{bachelorProject} 
\bibliography{bibloPartOne.bib}
\bibliographystyle{plain}
\end{document}